---
title: "practice_2"
author: "Mila pruiett"
date: "2023-01-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Practice with
- Packages
- Accessing specific columns in a data set
- Assigning variables
- Select
- Filtering


1. (Install if you haven't completed lesson 2) and load the tidyverse and palmerpenguins packages. 
```{r}
install.packages("tidyverse")
install.packages("palmerpenguins")

library("tidyverse")
library("palmerpenguins")
```


2. Assign the bill length column to a variable called penguinBillLength. Remember the data name is penguins. 
```{r}
penguinBillLength <- penguins$bill_length_mm
```


3. Assign the bill depth column to a variable called penguinBillDepth. 
```{r}
penguinBillDepth <- penguins$bill_depth_mm

```

For Questions 4 - 7, you can choose to either use the pipe %>% or not. Either way is great! 

4. Assign only the columns island, bill_length_mm, and bill_depth_mm to a new variable (name it whatever you'd like!). 
```{r}
# standard way
dataSubset <- select(penguins, island, bill_length_mm, bill_depth_mm)

# with the pipe
dataSubset2 <- penguins %>% select(island, bill_length_mm, bill_depth_mm)
```

5. Assign only the columns sex and year to the variable sexByYear. 
```{r}
# standard way
sexByYear <- select(penguins, sex, year)

# with the pipe
sexByYear2 <- penguins %>% select(sex, year)
```


6. Create a subset of the data that includes all the columns for only male Gentoo penguins with flipper lengths greater than 20 mm. 
```{r}
# standard way
longMales <- filter(penguins, sex == "male", flipper_length_mm > 20)

# with the pipe
longMales2 <- penguins %>% filter(sex == "male", flipper_length_mm > 20) 
```


7. Create a subset of the data that includes all penguins on Biscoe island with flipper lengths greater than 20 mm. Remove all of the NA values as well. 
```{r}

myPenguins <- na.omit(filter(penguins, island == "Biscoe", flipper_length_mm > 20))

```


Challenge: Using the pipe %>%, string together two commands with only one line of code to create a data set that includes only the columns: species, sex, and flipper length, with only Adelie penguins whose flippers are greater than 180 mm. 
```{r}
longAdelieSubset <- penguins %>% select(species, sex, flipper_length_mm) %>% filter(species == "Adelie", flipper_length_mm > 180)
```



