---
title: "practice_2"
author: "Mila pruiett"
date: "2023-01-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Practice with
- Packages
- Accessing specific columns in a data set
- Assigning variables
- Select
- Filtering


1. (Install if you haven't completed lesson 2) and load the tidyverse and palmerpenguins packages. 
```{r}

```


2. Assign the bill length column to a variable called penguinBillLength
```{r}

```


3. Assign the bill depth column to a variable called penguinBillDepth. 
```{r}

```

For Questions 4 - 7, you can choose to either use the pipe %>% or not. Either way is great! 

4. Assign only the columns island, bill_length_mm, and bill_depth_mm to a new variable (name it whatever you'd like!). 
```{r}

```

5. Assign only the columns sex and year to the variable sexByYear. 
```{r}

```


6. Create a subset of the data that includes all the columns only for male Gentoo penguins with flipper lengths greater than 20 mm. 
```{r}

```


7. Create a subset of the data that includes all penguins on Biscoe island with flipper lengths greater than 20 mm. Remove all of the NA values as well. 
```{r}

```


Challenge: Using the pipe %>%, string together two commands with only one line of code to create a data set that includes only the columns: species, sex, and flipper length, with only Adelie penguins whose flippers are greater than 180 mm. 
```{r}

```



