---
title: "practice_3"
author: "Mila pruiett"
date: "2023-01-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Practice with
* Packages
* Filtering
* Ggplot

### Instructions for plots
Each plot should have axis labels, a title, and use colors to illustrate the data.


1. (Install if you haven't completed lessons 2 or 3 or practice 2) and load the tidyverse and palmerpenguins packages. 
```{r}

```


2. Create a subset of the data that includes all the data from the years 2007 and 2008.
```{r}


```


3. Create a box plot of the bill lengths by male and female penguins of all species from the years 2007 and 2008. 
```{r}


```


4. Create a subset of the data that includes only the female penguins. 
```{r}

```


5. Create a box plot of the bill depth by species of only the female penguins. 
```{r}

```


6. Create a scatter plot of the relationship between bill length and bill depth for penguins on only Dream island and color by species.
```{r}

```

